From Education to Entrepreneurship

### 2014-12-06 index.Rmd
Deleted unnecessary variable in interactive webchart

# Melt CD df

CD2 <- melt(data = CD,
                  id.vars = c("Country", "Year"),
                  measure.vars = c("WayofTeaching", "PercentFear", "PercentNascent", "PercentPerceived",
                                   "PercentOwner", "PercentIntention", "PercentOpportunities"))

names(CD2) <- gsub("variable", "Survey Question", names(CD2))
names(CD2) <- gsub("value", "Response", names(CD2))

CD3 <- na.omit(CD2)

CD$Year <- as.Date(as.character(CD$Year), format = "%Y")

>>>>

# Set Year column as a date
CD$Year <- as.Date(as.character(CD$Year), format = "%Y")

# Dropp X column
CD$X <- NULL
